Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India

### 2018-11-06 draft.Rmd
Uppangala 0.1.9051 Guild position test and new map

```{r Uppangala, fig.cap="Canopy model of the 10-ha forest permanent plot in Uppangala, India. Preliminry figure to be improved."}
knitr::include_graphics("./data/test.png")
```

@@

>>>>

```{r Uppangala, fig.cap="Canopy model of the 10-ha forest permanent plot in Uppangala, India. Preliminry figure to be improved."}
knitr::include_graphics("./data/Plot.png")
```

@@

```{r positionTest, eval=F}
data <- pca.plot$data %>% 
  select(Comp.1, Comp.2, strata) %>% 
  rename(WES = Comp.1, LES = Comp.2)
test <- array(NA, c(2,2,n+1))
test[,,1] <- data %>% 
  group_by(strata) %>% 
  summarise_all(mean) %>% 
  select(-strata) %>% 
  as.matrix()
for(i in 1:n)
  test[,,i+1] <- data %>% 
  mutate(strata = sample(strata)) %>% 
  group_by(strata) %>% 
  summarise_all(mean) %>% 
  select(-strata) %>% 
  as.matrix()
data %>% 
  group_by(strata) %>% 
  summarise_all(mean) %>% 
  cbind(apply(test, 1:2, function(x){
    p <- rank(x)[1]/(n+1)
    if(p > 0.5)
      p <- 1 - p
    return(p)
  })) %>% 
  rename(WES.pval = `1`, LES.pval = `2`)
```
